\subsection{Receiver Survey, Study 1}
\subsubsection*{1. Screeners}
\begin{itemize}
    \item Eggplant question
    \item IP-address screener
    \item Crime story
    \begin{itemize}
        \item Filter on the easy questions: How was the person caught? [He left his ID]
        \item Code whether they get the harder question right (how much \$ did person walk away with)
    \end{itemize}
\end{itemize}

\subsubsection*{2. Demographics}
Please answer these background questions about yourself. 

\begin{itemize}
    \item What is your age? [textbox]
    \item What is your sex? [Male / Female / Other / Prefer not to say]
    \item Generally speaking, do you consider yourself a: [Democrat / Republican / Independent / Other]
    \item (if Democrat/Republican:) Would you call yourself a strong [Democrat/Republican] or
    a not very strong [Democrat/Republican]? [Strong Democrat / Not very strong
    Democrat / Not very strong Republican / Strong Republican]

    (if Independent/Other:) Do you think of yourself as closer to the
    Democratic or the Republican Party? [Lean Democrat / Independent / Lean
    Republican]
    \item In general, how would you describe your own political viewpoint?
    [Very liberal / Liberal / Moderate / Conservative / Very conservative]
    \item What is the highest level of education you have completed? [No high
    school/High school graduate/Some college/2-year/4-year/Post-grad] 
    \item What
    is your employment status? [Full-time / Part-time / Temporarily laid off /
    Unemployed / Retired / Permanently disabled / Homemaker / Student / Other]
    \item What racial or ethnic group best describes you?
    [White / Black / Hispanic / Asian / Native American / Mixed / Other / Middle Eastern]
    \item Here are 7 statements about the world. Please indicate how much you
    disagree or agree with each statement by selecting the appropriate box. A
    score of 1 indicates you strongly disagree with a statement, while a score
    of 6 means you strongly agree with the item.   
    \begin{itemize}
	\item I basically feel that the world is a fair place.
	\item I feel that people get what they deserve.
	\item I feel that people get what they are entitled to have.
	\item I feel that a person's efforts are noticed and rewarded.
	\item I feel that people who meet with misfortune have brought it on themselves.
	\item I feel that rewards and punishments are fairly given.
	\item I feel that people earn the rewards and punishments they get.
	\end{itemize}
    \item Here are 5 statements about your personality. Please indicate how
    much each statement is characteristic of you by selecting the appropriate
    box. A score of 1 indicates that a statement is extremely uncharacteristic
    of you, while a score of 5 means that a statement is extremely
    characteristic of you.
    \begin{itemize}
	\item Some of my friends think I am a hothead.
	\item I have trouble controlling my temper.
	\item Sometimes I fly off the handle for no good reason.
	\item I sometimes feel like a powder keg ready to explode.
	\item When frustrated, I let my irritation show.
    \end{itemize}
    \item Here are 7 statements about you and the world. Please indicate how
    much you disagree or agree with each statement by selecting the appropriate
    box. A score of 1 indicates you strongly disagree with a statement, while a
    score of 6 means you strongly agree with the item.
    \begin{itemize}
    \item I believe in luck.
	\item Some people are consistently lucky, and others are unlucky.
	\item There is such a thing as luck that favors some people, but not others.
	\item I tend to win games of chance.
	\item Luck works in my favor.
	\item I consistently have good luck.
	\item I often feel like it's my lucky day.
\end{itemize}
\end{itemize}

\subsubsection*{Qualtrics Variables}
\begin{itemize}
\item \{\$Task1\} = \{``Prediction''/''Counting''\} 
\item \{\$Task1description\} = \{``coin toss''
/ ``number counting''\} 
\item \{\$Task1short\} = \{``predict the outcome of a coin toss
performed by the computer'' / ``count how many odd numbers are contained in a
table generated by the computer''\} 
\item \{\$Task1long\} = \{``Specifically, you will
select the ``Heads'' or ``Tails'' button and then the computer will flip a fair
coin that will turn up heads or tails with equal probability'' / ``Specifically,
you will select one of two options to indicate how many odd numbers are in the
table''\} 
\item \{\$Task1correct\} = \{``correctly predict the coin toss'' / ``correctly
count how many odd numbers are in the table''\} 
\item \{\$Task1observer\} = \{``your
prediction and the outcome of the coin toss'' / ``your count of how many odd
numbers are in the table''\} 
\item \{\$Task1noun\} = \{``prediction'' / ``count''\}
\item \{\$Task1CorrectMsg\} = (if emotionalMsg = 0) \{``Your coin toss prediction matched the coin toss. You
earned \$0.25.'' / ``Your count was correct. You earned \$0.25.''\} or 
(if emotionalMsg = 1) \{``Congratulations! You won!''\} 
\item \{\$Task1IncorrectMsg\} = (if emotionalMsg = 1) \{``Your coin toss prediction did not match the coin toss.
You did not earn a bonus.'' / ``Your count was incorrect. You did not earn a
bonus.''\} or (if emotionalMsg = 1) \{``Too bad! You lost!''\}
\item \{\$Task2PartnerLong\} = \{``the person who was the messenger from part 1'' / ``a
new human participant selected at random (not the messenger from part 1)''\}
\item \{\$Task2PartnerShort\} \{``the messenger from part 1'' / ``another participant''\}
\end{itemize}

\subsubsection*{3. Instructions}
Please read these instructions carefully. You will complete a brief
comprehension quiz after each part of these instructions and you will earn an
\textbf{additional 5 cent bonus} for each quiz question you get right. 

\begin{description}[listparindent = 1.5em]
\item[Overview Instructions] \hspace{1cm}

Today you will earn 50 cents for participating in this task. You
will also have the opportunity to earn additional money based on how you do on
quizzes about these instructions as well as your and other participants'
decisions. This additional money will be paid to you as an MTurk bonus in the
next two weeks. 

Today's task is divided into three parts. We will describe \textbf{part
1} now, and then tell you about \textbf{parts 2 and 3} later.
\end{description}

\subsubsection*{Part 1 Instructions: \{\$Task1\} task}

In \textbf{part 1}, you will be randomly paired
with another human participant in this task who has the role of \textbf{messenger}. 

You
will then perform a \textbf{\{\$Task1\} task} where you \{\$Task1short\}. \{\$Task1long\}. You
will have 15 seconds to make your decision.

The \textbf{messenger} will then tell you the
outcome of the \{\$Task1\} task. If you \{\$Task1Correct\}, you will earn an additional
\textbf{50 cent bonus}. Otherwise, you earn \textbf{nothing}. 

The \textbf{messenger} will observe
\{\$Task1observer\}. They will communicate the outcome to you by clicking a button
that sends a standard message with the result. The messenger can only send an
accurate message. 

Specifically, if your \{\$Task1noun\} is correct,
you will receive this message: 

\textbf{\{\$Task1CorrectMsg\}}

If your \{\$Task1noun\} is incorrect,you will receive this message: 

\textbf{\{\$Task1IncorrectMsg\}}

Once you have finished reading these instructions, please proceed to the
3-question comprehension quiz on the next screen. For each question you get
right, you will earn \textbf{5 cents}.

\begin{description}
\item[Part 1 Quiz Question 1] \hspace{1cm}
\begin{enumerate}
\item In part 1, you will \ldots
\begin{enumerate}
    \item spin the wheel. 
\item \{\$Task1short\}. 
    \item open a virtual door. 
    \item click as many times as you can in 15 seconds. 
\end{enumerate}
\end{enumerate}

Feedback: \{Correct/Incorrect.\} In part 1, you will \{\$Task1short\}.

\item[Part 1 Quiz Question 2] \hspace{1cm}
\begin{enumerate}
\setItemnumber{2}
\item In part 1 (after this quiz), how much of a bonus will you earn?
\begin{enumerate}
    \item Nothing. 
    \item \$0.50 no matter what. 
    \item It depends on whether you \{\$Task1correct\}.
    \item It depends on whether your partner decides to send you a bonus.
\end{enumerate}
\end{enumerate}

Feedback: \{Correct/Incorrect.\} Your part 1 bonus depends on whether you
\{\$Task1correct\}. If you do so, you will earn \$0.50.

\item[Part 1 Quiz Question 3] \hspace{1cm} 
\begin{enumerate} \setItemnumber{3}
\item How do you find out whether you \{\$Task1correct\}?
\begin{enumerate} 
\item The computer will alert me.
\item I will find out in a later task.
\item I will never find out.
\item Another participant, the messenger, will send me a message.    
\end{enumerate} 
\end{enumerate}

Feedback: \{Correct/Incorrect.\} Another participant, the messenger, will send
you a message that tells you whether you \{\$Task1correct\}.
\end{description}

\subsubsection*{Part 1, messenger assignment}

You have been matched to another participant in this survey who will be the
\textbf{messenger}. 

[insert messenger figure]

You will see this icon when you interact with or answer questions about the
\textbf{messenger}.

\subsubsection*{(if counting = 0) Part 1, predict a coin tosss}
The computer will next flip a fair coin that will turn up heads or tails with
equal probability. 

If you predict the coin toss, you will earn 50 cents.
Otherwise, you will earn nothing. 

Which side do you choose? Select the ``Heads''
or ``Tails'' button to continue. 

You have 15 seconds to decide or you cannot
earn a bonus.

\subsubsection*{(if counting = 1) Part 1, choose which figure has more dots}

\textbf{The Number Counting Task} 

On each of the next two screens, you will see one 6x6
grid filled with numbers. Your job is to count how many odd numbers are in each
grid and determine which of the two grids has more odd numbers. 

You will have 10
seconds to look at each grid, and 15 seconds to decide which of the two grids
contains more odd numbers. 

If you correctly identify the grid with the most odd
numbers, you will earn 50 cents. Otherwise, you will earn nothing. 

[Next screens:
Show one 6x6 grid per page] 

[Decision screen] Now we will verify whether you
counted the odd numbers correctly. 

Which grid contains the most odd numbers?

\subsubsection*{Part 1, message}

The
\textbf{messenger} has sent you this message: 

\{If correct\}: \{\$Task1CorrectMsg\}

\{If
incorrect\}: \{\$Task1IncorrectMsg\}

[Only for participants randomly assigned to answering the attitudes questions
toward the messenger right after Task 1]

\begin{itemize}
	\item Here are 4 statements about the \textbf{messenger}. Please indicate how much each
statement matches the messenger's traits by selecting the appropriate box. A
score of 1 indicates that the messenger does not have that trait at all, while a
score of 7 means that a trait describes the messenger extremely well.
\\
{[insert messenger figure]}
\begin{itemize}
    \item How trustworthy is the messenger? 
    \item How nice is the messenger? 
    \item How likeable is the messenger? 
    \item How generous is the messenger?
\end{itemize}

\item Now, thinking about the message that you received about your performance
in task 1, please indicate how much you feel each emotion by selecting the
appropriate box. A score of 0 indicates that you do not feel an emotion at all,
while a score of 10 means you feel an emotion very much.
\begin{itemize}
\item How angry does the message make you feel?
\item How sad does the message make you feel?
\item How happy does the message make you feel?
\item How enthusiastic does the message make you feel?
\item How confused does the message make you feel?
\item How indifferent does the message make you feel?
\end{itemize}
\end{itemize}

\subsubsection*{Part 2 Instructions}

[If assigned to the messenger]

Now it is time for \textbf{Part 2} of this task. 
    
    In part 2, you will play three
    games with \textbf{\{\$Task2PartnerLong\}}. 
    
    [insert figure of messenger]
    
    We will describe each of the three games before you play them and you
    will answer a quiz question after each page of instructions. Then you will
    have the chance to play each game for a bonus.

    We will tell you the outcome of each game when we will pay you for this
    survey. 
    
    Please read these instructions carefully. For each question you get
    right, you will earn \textbf{5 cents}.

    [If assigned to another participant]

    Now it is time for \textbf{Part 2} of this task. 
        
        In part 2, you will play three
        games with \textbf{\{\$Task2PartnerLong\}}. 
        
        [insert figure of participant]
        
        We will describe each of the three games before you play them and you
        will answer a quiz question after each page of instructions. Then you will
        have the chance to play each game for a bonus.
    
        We will tell you the outcome of each game when we will pay you for this
        survey. 
        
        Please read these instructions carefully. For each question you get
        right, you will earn \textbf{5 cents}.

\begin{description}[listparindent = 1.5em]
    \item[Allocation game:]  \hspace{1cm}
    
    In the allocation game, we will give you an extra \$.50. You will decide
    how to allocate this extra money. Specifically, you can keep it all, or you
    can give some or all of it to your partner. Any money you keep will be given
    to you as a bonus, while any money you share will be given to
    \{\$Task2PartnerShort\} as a bonus. 
    
    You will indicate your choice by moving a
    slider that shows how much you wish to give to your partner. 
    
    [Slider label:
    How much of your \$.50 do you wish to give to your partner,
    \{\$Task2PartnerShort?\}]
\end{description}

\begin{description}[listparindent = 1.5em]
    \item[Spin the wheel game:] \hspace{1cm}
    
In the spin the wheel game, you have the chance to win an additional
    \$0.50 if you predict the outcome of a wheel spin correctly.  
      
    The wheel has ten
    numbers and only one number is the winning one. You pick a number, and if
    the wheel stops at that number, you earn extra \$0.50. Otherwise, you do not
    earn any extra money. We will communicate to you the result of the wheel
    spin at the end of this task. 
    
    You cannot spin the wheel yourself, however.
    Instead, you have to decide who spins the wheel on your behalf. 
    
    Specifically,
    you will have to choose whether you want the computer or your partner,
    \{\$Task2PartnerShort\}, to spin the wheel. 
    
    Do you prefer that the computer or
    your partner, \{\$Task2PartnerShort\}, spin the wheel? 
    
    \{``Computer'' /
    ``Partner''\}
\end{description}

\begin{description}[listparindent = 1.5em]
    \item[Directions game:] \hspace{1cm} 
    
    In the directions game, you can win up to extra \$0.50 depending on the
    decisions that you and your partner, \{\$Task2PartnerShort\}, will make. 
    
    You and
    your partner must choose whether to go up or down. 
    
    If you choose to go \textbf{up}:
    
    \begin{itemize}
    	\item and your partner also chooses to go up, each of you gets \$0.40.
    	\item and your partner chooses to go down, you get nothing and your
    partner gets \$0.40.
    \end{itemize}

    If you choose to go \textbf{down}:
    
    \begin{itemize}
    	\item and your partner chooses to go up, you get \$0.40 and your partner
    gets nothing.
    	\item and your partner also chooses to go down, each of you gets \$0.10.
    \end{itemize}

    You and your partner will choose without knowing each other's choice.

    Which direction do you choose? 
    
    \{``Up'' / ``Down''\}

    \item[Part 2 Quiz Question 1] \hspace{1cm}
    \begin{enumerate}
        \item True or false: In part 2, you partner is
        \{\$Task2PartnerShort\}?
        \begin{enumerate}
            \item True
            \item False
        \end{enumerate}
    \end{enumerate}

    Feedback: \{Correct/Incorrect.\} In part 2, you partner is
    \{\$Task2PartnerLong\}.

    \item[Part 2 Quiz Question 2] \hspace{1cm}
    \begin{enumerate} \setItemnumber{2}
        \item In the allocation game, what happens to any of the \$.50 you decide to keep?
        \begin{enumerate}
            \item It is paid to me as a bonus.
            \item It is paid to my partner as a bonus.
            \item Nothing, it simply disappears.            
        \end{enumerate}
    \end{enumerate}

    Feedback: \{Correct/Incorrect.\} In part 2, any money you decide to keep
    is paid to you as a bonus, while any money you give to your partner is paid
    to them as a bonus.

    \item[Part 2 Quiz Question 3] \hspace{1cm}
    \begin{enumerate} \setItemnumber{3}
        \item In the spin the wheel game, who spins the wheel whose outcome you are trying to predict?
        \begin{enumerate}
            \item I spin the wheel.
            \item The computer always spins the wheel.
            \item My partner always spins the wheel.
            \item I decide whether the computer or my partner spins the wheel.                   
        \end{enumerate}
    \end{enumerate}

    Feedback: \{Correct/Incorrect.\} You decide whether your partner or the
        computer spins the wheel.

    \item[Part 2 Quiz Question 4] \hspace{1cm}
    \begin{enumerate}\setItemnumber{4}
        \item In the directions game, how much money do you and
        \{\$Task2PartnerShort\} earn if you choose to go up?
        \begin{enumerate}
            \item Each of you gets \$0.40 regardless of what \{\$Task2PartnerShort\} chooses. 
            \item If \{\$Task2PartnerShort\} also chooses to go up, each of you gets \$0.40. 
            \item You get nothing regardless of what \{\$Task2PartnerShort\} chooses.
            \item You get \$0.10 and \{\$Task2PartnerShort\} gets \$0.40.                      
        \end{enumerate}
    \end{enumerate}

    Feedback: \{Correct/Incorrect.\} If \{\$Task2PartnerShort\} also chooses to go up,
    each of you gets \$0.40.
\end{description}

Now it is time to play the games. The instructions for each game are displayed
again on each page for your convenience. 

[On each of the next three screens,
participants play the dictator game, the spin the wheel game, and the prisoner's
dilemma game.] 

[After playing the games, participants who have not yet received
the attitudes and emotions questions answer them]

\subsubsection*{Part 3}

Lastly, please answer the following questions about your experience in the first
two parts of this survey.

\begin{itemize}
    \item Now, think back about your \{\$Task1description\} task in part 1. How fair do you think the \{\$Task1description\} task was? [7-point scale
    from ``Not very fair'' to ``Very fair'']
    \item How accurate was the message
    about the \{\$Task1observer\} sent by the messenger? [7-point scale from ``Not
    accurate at all'' to ``Extremely accurate'']
    \item How likely is that the messenger was a real person? [7-point scale
    from ``Not likely at all'' to ``Extremely likely'']
    \item How likely is it that
    the coin toss outcome was revealed by a computer? [7-point scale from
    ``Not likely at all'' to ``Extremely likely'']
\end{itemize}

\subsubsection*{End}

Thank you for participating in this study. To receive your payment, please copy
and paste this unique ID into MTurk: 

[randomly generated 5-digit ID]

\clearpage
\subsection{Messenger Survey}

(Only the parts that are unique to the messenger survey are presented below)

\subsubsection*{Send Message Screen}

Now, please select the button below to send an important
message to another MTurk participant, \textbf{the receiver}.

[insert figure of the receiver]

Your message will be
truthful and could deliver good news or bad news to them. 

You have no control
over what message you can send. 

[Button: Send a message delivering good or bad
news to the receiver.]

\subsubsection*{Spin the Wheel Screen} 

Now, please select the button below to spin a wheel of
fortune on behalf of another MTurk participant, \textbf{the receiver}. 

[insert figure of the receiver]

You will not know
the outcome of the wheel spin. Based on the outcome of the wheel spin, another
MTurk participant may earn bonus money. 

[Button: Click this button to spin a
wheel on behalf of another participant.]

\clearpage
\subsection{Receiver Survey, Study 2}

(Only the parts that are unique to the Study 2 survey are presented below)

\subsubsection*{Variables}
\begin{itemize}
\item \{\$Task1\} = \{``Prediction'' / ''Counting''\} 
\item \{\$Task1description\} = \{``coin toss''
/ ``number counting''\} 
\item \{\$Task1short\} = \{``predict the outcome of a coin toss
performed by the computer'' / ``count how many odd numbers are contained in a
table generated by the computer''\} 
\item \{\$Task1long\} = \{``Specifically, you will
select the ``Heads'' or ``Tails'' button and then the computer will flip a fair
coin that will turn up heads or tails with equal probability'' / ``Specifically,
you will select one of two options to indicate how many odd numbers are in the
table''\} 
\item \{\$Task1correct\} = \{``correctly predict the coin toss'' / ``correctly
count how many odd numbers are in the table''\} 
\item \{\$Task1observer\} = \{``your
prediction and the outcome of the coin toss'' / ``your count of how many odd
numbers are in the table''\} 
\item \{\$Task1noun\} = \{``prediction'' / ``count''\}
\item \{\$Task1CorrectMsg\} = \{SEE BELOW\}
\item \{\$Task1IncorrectMsg\} = \{SEE BELOW\} 
\item \{\$Task2PartnerLong\} = \{``the
person who was the messenger from part 1'' / ``a new human participant selected
at random (not the messenger from part 1)''\} 
\item \{\$Task2PartnerShort\} \{``the
messenger from part 1'' / ``another participant''\} 
\item \{\$Instructions1\} = \{SEE
BELOW\}
\end{itemize}

\subsubsection*{\{\$Instructions1\}}

\begin{itemize}
\item -1 you will earn an additional 50 cents bonus and the messenger will not
earn any money for delivering this message. Otherwise, you earn nothing but the
messenger will earn a 50 cent bonus for delivering this message.

\item -0.1 you will earn an additional 50 cents bonus and the messenger will
not earn any money for delivering this message. Otherwise, you earn nothing but
the messenger will earn a 5 cent bonus for delivering this message.

\item 0 you will earn an additional 50 cent bonus and the messenger will not
earn any money for delivering this message. Otherwise, you earn nothing and the
messenger will not earn any money for delivering this message.

\item 0.1 you will earn an additional 50 cents bonus and the messenger will
earn a 5 cent bonus for delivering this message. Otherwise, you earn nothing and
the messenger will not earn any money for delivering this message.

\item 1 you will earn an additional 50 cents bonus and the messenger will earn
a 50 cent bonus for delivering this message. Otherwise, you will earn nothing
and the messenger will not earn any money for delivering this message.
\end{itemize}

\subsubsection*{\{\$Task1CorrectMsg\}}
\begin{itemize}
\item -1 ``Your coin toss prediction matched the coin toss. You earned \$0.50 but I
did not earn any money for delivering this message.'' / ``Your count was correct.
You earned \$0.50 but I did not earn any money for delivering this message.''

\item -0.1 ``Your coin toss prediction matched the coin toss. You earned \$0.50 but I
did not earn any money for delivering this message.''/ ``Your count was correct.
You earned \$0.50 but I did not earn any money for delivering this message.''

\item 0 ``Your coin toss prediction matched the coin toss. You earned \$0.50 but I did
not earn any money for delivering this message.''/ ``Your count was correct. You
earned \$0.50 and I did not earn any money for delivering this message.''

\item 0.1 ``Your coin toss prediction matched the coin toss. You earned \$0.50 and I
earned \$0.05 for delivering this message.'' / ``Your count was correct. You
earned \$0.50 and I earned \$0.05 for delivering this message.''

\item 1 ``Your coin toss prediction matched the coin toss. You earned \$0.50 and I
earned \$0.50 for delivering this message.'' / ``Your count was correct. You
earned \$0.50 and I earned \$0.50 for delivering this message.''
\end{itemize}

\subsubsection*{\{\$Task1IncorrectMsg\}}
\begin{itemize}
\item -1 ``Your coin toss prediction did not match the coin toss. You did not earn any
money but I earned \$0.50 for delivering this message.'' / ``Your count was
incorrect. You did not earn any money but I earned \$0.50 for delivering this
message.'' 

\item -0.1 ``Your coin toss prediction did not match the coin toss. You did
not earn any money but I earned \$0.05 for delivering this message.'' / ``Your
count was incorrect. You did not earn any money but I earned \$0.05 for
delivering this message.'' 

\item 0 ``Your coin toss prediction did not match the coin
toss. You did not earn any money and I did not earn any money for delivering
this message.''/ ``Your count was incorrect. You did not earn any money and I
did not earn any money for delivering this message.'' 

\item 0.1 ``Your coin toss
prediction did not match the coin toss. You did not earn any money and I did not
earn any money for delivering this message.''/ ``Your count was incorrect. You
did not earn any money and I did not earn any money for delivering this message.'' 

\item 1 ``Your coin toss prediction did not match the coin toss. You did not earn
any money and I did not earn any money for delivering this message.'' / ``Your
count was incorrect. You did not earn any money and I did not earn any money for
delivering this message.''
\end{itemize}

\subsubsection*{Part 1 Instructions: \{\$Task1\} task}

In \textbf{part 1}, you will be randomly paired
with another MTurk participant in this task who has the role of \textbf{messenger}. 

You 
will then perform a \textbf{\{\$Task1\} task} where you \{\$Task1short\}. \{\$Task1long\}. You
will have 15 seconds to make your decision. 

The \textbf{messenger} will then tell you the
outcome of the \{\$Task1\} task. 

If you \{\$Task1Correct\}, \{\$Instructions1\}.

Your partner will observe
\{\$Task1observer\}. They will communicate the outcome to you by clicking a
button that sends a standard message with the result. The messenger can only
send an accurate message.

Specifically, if your \{\$Task1noun\}
is correct, you will receive this message: \textbf{\{\$Task1CorrectMsg\}}. 

If your
\{\$Task1noun\} is incorrect, you will receive this message: \textbf{\{\$Task1IncorrectMsg\}}.

Once you have finished reading these instructions, please proceed to the
3-question comprehension quiz on the next screen. For each question you get
right, you will earn \textbf{5 cents}.

\begin{description}
\item[Part 1 Quiz Question 4] \hspace{1cm} 
\begin{enumerate} \setItemnumber{4}
\item How much does the messenger get paid for delivering this message?
\begin{enumerate}
\item The messenger [-1: earns a 50 cent bonus if you fail to \{\$Task1correct\} /
-0.1: earns a 5 cent bonus if you fail to \{\$Task1correct\} / 0: does not earn any
money for delivering this message / 0.1: earns a 5 cent bonus if you
\{\$Task1correct\} / 1: earns a 50 cent bonus if you \{\$Task1correct\}].
\item The messenger draws a card which reveals their payment.
\item I will never find out.
\item The messenger gets paid a fixed sum for delivering this message no matter what.
\end{enumerate} 
\end{enumerate}

Feedback: \{Correct/Incorrect.\} The messenger [-1: earns a 50 cent bonus if you
fail to \{\$Task1correct\} / -0.1: earns a 5 cent bonus if you fail to
\{\$Task1correct\} / 0: does not earn any money for delivering this message / 0.1:
earns a 5 cent bonus if you \{\$Task1correct\} / 1: earns a 50 cent bonus if you
\{\$Task1correct\}].

\end{description}

\subsubsection*{Part 3}

Now, think back about the game you just played. Suppose you were in the role of
the messenger rather than the receiver.

\begin{itemize}
    \item Do you think the receiver would like you more or less if you
    were the messenger who informed them that they \underline{lost}? 
    [5-point scale from ``The receiver would like me a lot less'' to ``The
    receiver would like me a lot more.''
    \item What makes you think so? [textbox]
    \item Do you think the receiver would like you more or less if you
    were the messenger who informed them that they \underline{won}? [5-point
    scale from ``The receiver would like me a lot less'' to ``The receiver would
    like me a lot more.''
    \item What makes you think so? [textbox]
    \item To what extent do you agree or disagree with the following statements:
    \begin{itemize}
        \item ``A messenger should be \textbf{rewarded} for delivering \textbf{good news} for
        which they are not responsible.'' [5-point scale from strongly agree to
        strongly disagree]
    \end{itemize}
    \begin{itemize}
    	\item ``A messenger should be \textbf{punished} for delivering \textbf{bad news} for which
    they are not responsible.'' [5-point scale from strongly agree to
    strongly disagree]
    \end{itemize}
\end{itemize}